Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-08-29 manuscript.tex
puliendo las referencias y modificado el plot 1

@@

@@

We illustrate in the Fig.~\ref{F_growing_sphere} the schematic

@@

@@

In the Fig.~\ref{F_abcd}, we show a schematic representation of two

@@

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{growingsphere.pdf}
   \caption{Schematic representation of the growing communicating
   sphere, over the space--time diagrams, where time is represented on
   the horizontal direction, and space is represented in the vertical
   direction.  In (a) the sphere is
   growing as the surface of first contact has not reached the maximum
   distance.  In (b) it has reached the maximum distance, so that it
   remains at the same size.  After a Doomsday event, the signals can
   still be observed, but the surface of last contact grows }
   \label{F_growing_sphere}
\end{figure}

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{abcd.pdf}
   \caption{Schematic representation of two emitters, $E_1$ and $E_2$,
   that reach each other at different times.  The time span for $E_i$
   is $(A_i, D_i)$, for $i=\{1,2\}$.  Emitter $i$ can listen to
   emitter $j$ between $C_{ij}$ and $B_{ij}$.
   The type and length of causal contact in both directions depend on
   the distance and time lag between the awakening events, the maximum
   distance that a signal can reach and the time period in which each
   emitter is active.}
   \label{F_abcd}
\end{figure}

The temporal structure of the process is defined by two distribution
parameters that represent the mean time interval that an intelligent
civilization can emit and receive signals, and the mean time interval
between the emergence of an intelligent comunicating civilization and
the next one.
%
The spatial structure of the simulation is given by the size and shape
of the Galactic Habitable Zone and the maximum distance a signal can
travel to be detected.
%
The parameters for the temporal distributions also determine the
spatial properties since the density of active cetis in the Galaxy
depend on these two parameters.
%
For example, a small $\tau_a$ and a large $\tau_s$ will produce a
Galaxy densely populated woth CETIs, and viceversa.
%
Also, some hypotheses must be made in order to complete the
simulation.
%
Firstly, we assume that the distribution of the appeareance of new
CETIs is a stationary Poisson distribution.
%
Regarding the duration of a CETI, we propose that the distribution of
the duration of CETIs is a stationary exponential distribution.
%
\citet{balbi_impact_2018} stress the fact that it would be desirable to arrive
at a theoretical statistical distribution of the lifespan of
civilizations, preferentially on the basis of the underlying
astrophysical and biological processes.
%
\citet{maccone_lognormals_2014} argues that this distribution should be a log normal.
(EXPAND)

@@

>>>>

%% Stochastic estimation of the waiting time for the first causal contact
%% with an extraterrestrial intelligence

@@

HACER DISCUSION FUERTE DE ESTOS PAPERS: \cite{balbi_impact_2018,cirkovic_temporal_2004,grimaldi_signal_2017,smith_broadcasting_2009}

@@

We illustrate in the Fig.~\ref{F_scheme} the schematic

@@

% Schematic representation of the growing communicating
%   sphere, over the space--time diagrams, where time is represented on
%   the horizontal direction, and space is represented in the vertical
%   direction.  In (a) the sphere is
%   growing as the surface of first contact has not reached the maximum
%   distance.  In (b) it has reached the maximum distance, so that it
%   remains at the same size.  After a Doomsday event, the signals can
%   still be observed, but the surface of last contact grows.
%   %
%   Schematic representation of two emitters, $E_1$ and $E_2$,
%   that reach each other at different times.  The time span for $E_i$
%   is $(A_i, D_i)$, for $i=\{1,2\}$.  Emitter $i$ can listen to
%   emitter $j$ between $C_{ij}$ and $B_{ij}$.
%   The type and length of causal contact in both directions depend on
%   the distance and time lag between the awakening events, the maximum
%   distance that a signal can reach and the time period in which each
%   emitter is active.

@@

We also show in this Figure a schematic representation of two

@@

%\begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth]{growingsphere.pdf}
%   \caption{Schematic representation of the growing communicating
%   sphere, over the space--time diagrams, where time is represented on
%   the horizontal direction, and space is represented in the vertical
%   direction.  In (a) the sphere is
%   growing as the surface of first contact has not reached the maximum
%   distance.  In (b) it has reached the maximum distance, so that it
%   remains at the same size.  After a Doomsday event, the signals can
%   still be observed, but the surface of last contact grows }
%   \label{F_growing_sphere}
%\end{figure}
%
%  
%\begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth]{abcd.pdf}
%   \caption{Schematic representation of two emitters, $E_1$ and $E_2$,
%   that reach each other at different times.  The time span for $E_i$
%   is $(A_i, D_i)$, for $i=\{1,2\}$.  Emitter $i$ can listen to
%   emitter $j$ between $C_{ij}$ and $B_{ij}$.
%   The type and length of causal contact in both directions depend on
%   the distance and time lag between the awakening events, the maximum
%   distance that a signal can reach and the time period in which each
%   emitter is active.}
%   \label{F_abcd}
%\end{figure}

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{scheme.pdf}
   \caption{Space--time diagrams showing a schematic representation of the 
   different stages in the development of a communicating
   civilization, the growing communicating sphere (a) and the temporal
   intervals for the communication between two civilizations (b).
   %
   In the upper panel (a), the sphere the encloses the region which is
   causally connected to the emitter grows until it reaches the
   $D_{max}$ distance.  After the $D$ event, that region is limited by
   the surface of last contact.
   %
   The scheme in the lower panel (b) represents
   two communicating civilizations that have
   causal contact in both directions}   
   \label{F_scheme}
\end{figure}

The temporal structure of the process is defined by two distribution
parameters that represent the mean time interval that an intelligent
civilization can emit and receive signals, and the mean time interval
between the emergence of an intelligent comunicating civilization and
the next one.
%
The spatial structure of the simulation is given by the size and shape
of the Galactic Habitable Zone and the maximum distance a signal can
travel to be detected.
%
The parameters for the temporal distributions also determine the
spatial properties since the density of active cetis in the Galaxy
depend on these two parameters.
%
For example, a small $\tau_a$ and a large $\tau_s$ will produce a
Galaxy densely populated woth CETIs, and viceversa.
%
Also, some hypotheses must be made in order to complete the
simulation.
%
\citet{forgan_spatiotemporal_2011} argues that the times at which
different civilizations become intelligent 
follow a Gaussian distribution, and then the distribution of
inter-arrival times is an inverse exponential.
%
We chose to assume that the distribution of the times of A events is a
stationary Poisson process, and then the distribution of the times between the
appeareance of new consecutive CETIs is exponential.
%
Regarding the duration of a CETI, we propose that the distribution of
the duration of CETIs is a stationary exponential distribution.
%
\citet{balbi_impact_2018} stress the fact that it would be desirable to arrive
at a theoretical statistical distribution of the lifespan of
civilizations, preferentially on the basis of the underlying
astrophysical and biological processes.
%
\citet{maccone_lognormals_2014} argues that this distribution should be a log normal.
(EXPAND)

@@

%%% comparar con el stochsatic cellular automata
% ver libro Solving Fermi paradox, sec. 27.3.1
